---
title: "dieroller"
author: "JOSH SEO"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dieroller}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(dieroller)
```


## Die Rolling
The package '"dieroller"' is a minimal implementation for simulating rolling a die a given number of times and to visualize the relative frequencies in such a series of rolls.

## Creating a 'die'
The first step is to create a '"die"' object with the function 'die()':
```{r}
fair_die <- die()
fair_die
```

In order to create a different "die" object write:
'die()' function should have two arguments:
sides: vector of six elements, by default numbers 1, 2, 3, 4, 5, 6.
prob: vector of probabilities for each side (all equal to 1/6 by default)
An auxiliary function check_sides(), called by die(), checks the validity of the argument sides.
An auxiliary function check_prob(), called by die(), checks the validity of the argument prob.
```{r}
# die with non-standard sides
weird_die <- die(sides = c('i', 'ii', 'iii', 'iv', 'v', 'vi'))
weird_die

# create a loaded die
loaded_die <- die(prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))
loaded_die
```

## Rolling the die
To roll an object "die", you will have to use 'roll()' function.
'roll()' function should have two arguments:
die: object of class "die".
times: number of times to roll the die (default value of 1).
An auxiliary function check_times(), called by roll(), checks the validity of the argument times.
The output of roll() will be a list containing:
rolls: vector with outputs of the rolls
sides: vector with the sides of the die
prob: vector with probabilities for each side of the die
total: total number of rolls (i.e. times)

Here’s a basic example for 'roll()':
```{r}
# roll fair die 50 times
fair_die <- die()
set.seed(123)
fair50 <- roll(fair_die, times = 50)
fair50
```

## Summarize
'summary()' for "roll" objects a "summary.roll" object. 
The output is a data frame with 3 columns:
side: the sides of the rolled die.
count: the frequency (count) of each side of the rolled die.
prop: the relative frequency (proportion) of each side of the rolled die.
Example:
```{r}
set.seed(123)
fair_50rolls <- roll(fair_die, times = 50)
fair50_sum <- summary(fair_50rolls)
fair50_sum
```

## Plotting
'plot()' for "roll" objects returns a barchart of frequencies (relative frequencies of each side of the "die"). 
```{r}
# plot method
plot(fair_50rolls)
```

## Extra functions
To extract a desired value of a given roll:
```{r}
# roll a fair die 500 times
set.seed(123)
fair_die <- die()
fair500 <- roll(fair_die, times = 500)
# extracting roll in position 500
fair500[500]
```

To replace a value of a given roll with a desired value:
```{r}
# replacing the 500th roll
fair500[500] <- 1
fair500[500]
```

To add a desired number(times) of rolls to a given roll:
```{r}
# adding 100 rolls
fair600 <- fair500 + 100
summary(fair600)
```

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
